### 2015-12-07 ada-ftrl.tex
Replace subscript "s" with "i"
Add limit explanations and limit lemma

The sequence $\{\Delta_t\}_{t=0}^\infty$ is non-negative and non-decreasing.
Also, $\Delta_t$ as a function of $\{\ell_s\}_{s=1}^t$ is positive homogenous
of degree one, making the algorithm scale-free.

If $\Delta_{i-1} = 0$, we define $\Delta_{i-1}
\Breg_{R^*}(\frac{-L_i}{\Delta_{i-1}}, \frac{-L_{i-1}}{\Delta_{i-1}})$ as
$\lim_{a \to 0^+} a \Breg_{R^*}(\frac{-L_i}{a}, \frac{-L_{i-1}}{a})$ which
always exists and is finite; see~\ref{section:limits}.  Similarly,
when $\Delta_{t-1} = 0$, we define $w_t = \argmin_{w \in K} \langle L_{t-1}, w
\rangle$ where ties among minimizers are broken by taking the one with the
smallest value of $R(w)$, which is unique due to strong convexity; this is the
same as $w_t = \lim_{a \to 0^+} \argmin_{w \in K} (\langle L_{t-1}, w \rangle +
aR(w))$.

@@

\begin{proof}
Let $R_t(w) = \Delta_{t-1} R(w)$. Since $R$ is non-negative,
$\{R_t\}_{t=1}^\infty$ is non-decreasing.  Hence, $R_t^*(\ell) \ge
R_{t+1}^*(\ell)$ for every $\ell \in V^*$ and thus $R_t^*(-L_t) -
R_{t+1}^*(-L_t) \ge 0$.  So, by Lemma~\ref{lemma:generic-regret-bound},
\begin{equation}
\label{equation:regret-bound-inequality}
\Regret_T(u) \le R_{T+1}(u) + R_1^*(0) + \sum_{t=1}^{T} \Breg_{R_t^*}(-L_t, -L_{t-1}) \; .
\end{equation}
Since, $\Breg_{R_t^*}(u,v) = \Delta_{t-1} \Breg_{R^*}(\frac{u}{\Delta_{t-1}},
\frac{v}{\Delta_{t-1}})$ by definition of Bregman divergence and Part 8 of
Proposition~\ref{proposition:conjugate-properties}, we have $\sum_{t=1}^T
\Breg_{R_t^*}(-L_t, -L_{t-1}) = \Delta_T$.
\end{proof}

>>>>

The sequence $\{\Delta_t\}_{t=0}^\infty$ is non-negative and non-decreasing.
Also, $\Delta_t$ as a function of $\ell_1, \ell_2, \dots, \ell_t$ is positive homogenous
of degree one, making the algorithm scale-free.

If $\Delta_{i-1} = 0$, we define $\Delta_{i-1}
\Breg_{R^*}(\frac{-L_i}{\Delta_{i-1}}, \frac{-L_{i-1}}{\Delta_{i-1}})$ as
$\lim_{a \to 0^+} a \Breg_{R^*}(\frac{-L_i}{a}, \frac{-L_{i-1}}{a})$ which
always exists and is finite; see Lemma~\ref{lemma:limit-bregman-divergence}
in~\ref{section:limits}.  Similarly, when $\Delta_{t-1} = 0$, we define $w_t =
\argmin_{w \in K} \langle L_{t-1}, w \rangle$ where ties among minimizers are
broken by taking the one with the smallest value of $R(w)$, which is unique due
to strong convexity; as we show in Lemma~\ref{lemma:prediction-limit-existence}
in~\ref{section:limits}, this is the same as $w_t = \lim_{a \to 0^+}
\argmin_{w \in K} (\langle L_{t-1}, w \rangle + aR(w))$.

@@

\begin{proof}
Let $R_t(w) = \Delta_{t-1} R(w)$. Since $R$ is non-negative,
$\{R_t\}_{t=1}^\infty$ is non-decreasing.  Hence, $R_t^*(\ell) \ge
R_{t+1}^*(\ell)$ for every $\ell \in V^*$ and thus $R_t^*(-L_t) -
R_{t+1}^*(-L_t) \ge 0$.  So, by Lemma~\ref{lemma:generic-regret-bound},
\begin{equation}
\label{equation:regret-bound-inequality}
\Regret_T(u) \le R_{T+1}(u) + R_1^*(0) + \sum_{t=1}^{T} \Breg_{R_t^*}(-L_t, -L_{t-1}) \; .
\end{equation}
Technically, \eqref{equation:regret-bound-inequality} is not justified since $R_t$
might not be strongly convex. This happens when $\Delta_{t-1} = 0$. In order to justify
\eqref{equation:regret-bound-inequality}, we consider a different algorithm
that initializes $\Delta_0 = \epsilon$ where $\epsilon > 0$; that ensures that $\Delta_{t-1} > 0$ and $R_t$ is strongly convex.
Applying  Lemma~\ref{lemma:generic-regret-bound} and then taking limit $\epsilon \to 0$,
yields \eqref{equation:regret-bound-inequality}.

Since, $\Breg_{R_t^*}(u,v) = \Delta_{t-1} \Breg_{R^*}(\frac{u}{\Delta_{t-1}},
\frac{v}{\Delta_{t-1}})$ by definition of Bregman divergence and Part 8 of
Proposition~\ref{proposition:conjugate-properties}, we have $\sum_{t=1}^T
\Breg_{R_t^*}(-L_t, -L_{t-1}) = \Delta_T$.
\end{proof}

### 2015-12-07 limits.tex
Add limit explanations and limit lemma

\begin{lemma}
\label{lemma:limit-existence}
Let $K$ be a non-empty bounded closed convex subset of a finite dimensional
normed real vector space $(V, \|\cdot\|)$.  Let $R:K \to \R$ be a strongly
convex lower semi-continuous function bounded from above. Then, for any $x,y
\in V^*$,
$$
\lim_{a \to 0^+} a \Breg_{R^*}(x/a, y/a) = \langle x, u - v \rangle \\
$$
where
\begin{align*}
u = \lim_{a \to 0^+} \argmin_{w \in K} \left( a R(w) - \langle x, w \rangle \right)
\quad \text{and} \quad
v = \lim_{a \to 0^+} \argmin_{w \in K} \left( a R(w) - \langle y, w \rangle \right) \; .
\end{align*}
\end{lemma}

>>>>

In this section we show that prediction of \textsc{AdaFTRL} is correctly
defined when the regularizer is multiplied by zero.

\begin{lemma}[Prediction for Zero Regularizer]
\label{lemma:prediction-limit-existence}
Let $K$ be non-empty bounded closed convex subset of a finite dimensional normed real vector space $(V, \|\cdot\|)$.
Let $R:K \to \R$ be strictly convex and lower semi-continuous, and let $L \in V^*$. The limit
\begin{equation}
\label{equation:limit}
\lim_{\eta \to +\infty}
\argmin_{w \in K} \left( \langle L, w \rangle + \frac{1}{\eta} R(w) \right)
\end{equation}
exists and it is equal to the unique minimizer of $R(w)$ over the set (of minimizers)
$$
\left\{ w \in K ~:~ \langle L, w \rangle = \inf_{v \in K} \langle L, v \rangle \right\} \; .
$$
\end{lemma}

Before we give the proof, we illustrate the lemma on a simple
example.  Let $K = [-1,1]^2$ be the unit square in $\R^2$ and let
$R(w) = \|w\|_2^2$. Let $L = (1,0)$. The minimizers are
$$
\argmin_{w \in K} \langle L, w \rangle = \{ (-1,y) ~:~ y \in [-1,1] \} \; .
$$
The minimizer with smallest value of $R(w)$ is $(-1,0)$. Hence the lemma implies
that
$$
\lim_{\eta \to +\infty} \argmin_{w \in K}
\left( \langle L, w \rangle + \frac{1}{\eta} \|w\|_2^2 \right) = (-1, 0) \; .
$$

\begin{proof}
Without loss of generality, we can assume that $R(w)$ is non-negative for any $w \in K$.
For otherwise, we can replace $R(w)$ with $R'(w) = R(w) - \inf_{v \in K} R(v)$.

Since $K$ is a non-empty bounded closed convex subset of a finite dimensional normed vector space, it is compact
and $r^* = \min_{w \in K} \langle L, w \rangle$ exists and is attained at some $w \in K$. Consider the hyperplane
$$
H = \{ w \in V ~:~ \langle L, w \rangle = r^* \} \; .
$$
The intersection $H \cap K$ is a non-empty compact convex set.
Let
$$
v^* = \argmin_{v \in K \cap H} R(v) \; .
$$
The existence of $v^*$ follows from compactness of $H \cap K$ and lower
semi-continuity of $R(v)$.  Uniqueness of $v^*$ follows from
strict convexity of $R(v)$. We show that the limit (\ref{equation:limit})
equals $v^*$.

By the definition of $H$,
\begin{equation}
\label{equation:limit-is-minimizer}
v^* \in \argmin_{w \in K} \ \langle L, w \rangle \; .
\end{equation}
Let $S = \{ w \in K ~:~ R(w) \le R(v^*) \}$. Since $R(w)$ is lower semi-continuous $S$
is closed. Since $R(w)$ is strictly convex, $S \cap H = \{v^*\}$.

For any $\eta > 0$, let
$$
w(\eta) = \argmin_{w \in K} \left( \langle L, w \rangle + \frac{1}{\eta} R(w) \rangle \right) \; .
$$
We prove that $w(\eta) \in S$. Indeed, by optimality of $v^*$ and $w(\eta)$
$$
\frac{1}{\eta} R(w(\eta))  + \langle L, w(\eta) \rangle
\le
\frac{1}{\eta} R(v^*)  + \langle L, v^* \rangle
\le
\frac{1}{\eta} R(v^*)  + \langle L, w(\eta) \rangle \; .
$$
and hence $R(w(\eta)) \le R(v^*)$.

By non-negativity of $R$ and optimality of $w(\eta)$ we have
$$
\langle L, w(\eta) \rangle
\le \langle L, w(\eta) \rangle + \frac{1}{\eta} R(w(\eta))
\le \langle L, v^* \rangle + \frac{1}{\eta} R(v^*) \; .
$$
Taking the limit $\eta \to +\infty$, we see that
$$
\lim_{\eta \to +\infty} \langle L, w(\eta) \rangle \le
\lim_{\eta \to +\infty} \left( \langle L, v^* \rangle + \frac{1}{\eta} R(v^*) \right)
= \langle L, v^* \rangle \; .
$$
From~(\ref{equation:limit-is-minimizer}) we have
$\langle L, v^* \rangle \le \langle L, w \rangle$ for any $w$, and therefore
\begin{equation}
\label{equation:limit-equality}
\lim_{\eta \to +\infty} \langle L, w(\eta) \rangle = \langle L, v^* \rangle \; .
\end{equation}

Consider any sequence $\{\eta_t\}_{t=1}^\infty$ of positive numbers approaching
$+\infty$.  Since $K$ is compact, $w(\eta_t)$ has a convergent subsequence.
Thus $\{w(\eta_t)\}_{t=1}^\infty$ has at least one accumulation point; let
$w^*$ be any of them. We will show that $w^* = v^*$.

Consider a subsequence $\{\xi_t\}_{t=1}^\infty$ of
$\{\eta_t\}_{t=1}^\infty$ such that $\lim_{t \to \infty} w(\xi_t) = w^*$.
Since $w(\xi_t) \in S$ and $S$ is closed, $w^* \in S$.
From (\ref{equation:limit-equality}) we have $\langle L, w^*
\rangle = \langle L, v^* \rangle$ and hence $w^* \in H$. Thus $w^* \in S \cap H$.
Since $v^*$ is the only point in $S \cap H$ we must have $w^* = v^*$.
\end{proof}

\begin{lemma}[Limit of Bregman Divergence]
\label{lemma:limit-bregman-divergence}
Let $K$ be a non-empty bounded closed convex subset of a finite dimensional
normed real vector space $(V, \|\cdot\|)$.  Let $R:K \to \R$ be a strongly
convex lower semi-continuous function bounded from above. Then, for any $x,y
\in V^*$,
$$
\lim_{a \to 0^+} a \Breg_{R^*}(x/a, y/a) = \langle x, u - v \rangle \\
$$
where
\begin{align*}
u = \lim_{a \to 0^+} \argmin_{w \in K} \left( a R(w) - \langle x, w \rangle \right)
\quad \text{and} \quad
v = \lim_{a \to 0^+} \argmin_{w \in K} \left( a R(w) - \langle y, w \rangle \right) \; .
\end{align*}
\end{lemma}
